\documentclass[margin,line]{res}
\usepackage{hyperref}
\usepackage{url}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\topmargin=0in
\topskip=0in
 
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.2in}}}{\end{list}}
    
\begin{document}

\name{\LARGE Hamilton Reid Baker} \hfill {\em \today}

\begin{resume}
\section{\sc Contact Information}

\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
Programer             & {Phone:}  (772) 202-2537 \\
Georgia Tech
 & {E-mail:}  hamiltonbaker@gatech.edu\\
3205 Wareham Circle. \\
Richardson, TX, 75082  & {Website:} \url{https://github.com/reidbaker}
\end{tabular}


\section{\sc Interests}

Software engineering, Web development

\section{\sc Education}
{\bf Georgia Institute of Technology}, Atlanta, GA. USA \hfill August 2008 -- present\\

Name of the Degree \hfill(GPA 3.02/4.0)

{\bf Programming and Scripting Languages}:  C, C\#, Python, SQL, HTML, XML, PHP\\
{\bf Operating Systems}: Windows, Linux, Mac OSX\\
{\bf Tools}: Latex, Subversion, Git, Emacs \\
%%%%%%
\section{\sc Professional Experience}
%%%%%%
{\bf Yelp}, San Fransisco, CA. USA. \hfill{January 2012 -- April 2012}\\
{\em Software Developer}\hfill\\
    \begin{list2} %Job Description%
    \item Worked as part of a team supporting internal tools used by
      non-engineers \\
    \item Responsible for fixing bugs \\
\end{list2}
%%%%%%
{\bf SimpleC}, Atlanta, GA. USA. \hfill{Summer 2011}\\
{\em Mobile Application Internship} \\
\begin{list2} %Job Description%
    \item Worked as part of a team of four inters to port and existing
      application to Andoid Tablets. \\
    \item We added functionality to the mobile platform and enhanced the
      original design by addressing feedback gained through interaction
      with users.\\
\end{list2}
{\bf Sagepath}, Atlanta, GA. USA. \hfill{Fall 2010}\\
{\em Software Development Internship} \\
\begin{list2} %Job Description%
    \item Developed a site redesign as part of a team \\
    \item Developed .net applications \\
    \item Debugged and fixed Cross-Browser Comparability issues \\
\end{list2}
{\bf Research Assistant}, Atlanta, GA. USA. \hfill{Summer 2010}\\
\begin{list2} %Job Description%
    \item Feasibility tested Appinventor deployment as a tool to
      enhance teaching students in non-computing majors.
    \item Studied then suggested modifications for textbook on Appinventor.\\
\end{list2}
%%%%%%
\section{\sc Projects}
{\bf Project Name}\\
Project Details\\

{\bf Project Name}\\
Project Details\\

\section{\sc Publications}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{list2}
\item LastName Author1, First initial., LastName Author2, First initial.,  "Title",{\em Where published}, Date
\item LastName Author1, First initial., LastName Author2, First initial.,  "Title",{\em Where published}, Date
\end{list2}


\section{\sc References }
Available upon request.

\end{resume}
\end{document}





